Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices

### 2016-11-11 Presentation/gpm_november2016_vianello.tex
staring to add slides after background 	modified:   gpm_november2016_vianello.tex

  \section{Open issue}
  \begin{frame}{Open and unresolved issues}
  \setbeamercovered{transparent}
  \begin{enumerate}[<+(1) | invisible@-+>]
    \item Does $\Lambda_{div}$ unify the picture among the devices?
      \alert{No, a dependence on neutral pressure is likely to play a role}
    \item If neutrals play a role is it at the divertor and/or at the midplane?
      \alert{Contradictory results if one include experiments with
        midplane puffing, JET and EIRENE simulations}
    \item Does L$_\parallel$ play any role? \alert{So far TCV suggests no
      dependence from f$_x$ scan but both TCV and MAST observe an
      I$_p$ dependence. MAST clearly state filament $\sigma_{\perp}$
      increases with L$_{\parallel}$ }
    \item Is cooling the divertor with fueling or with equivalent? \alert{Contradictory observations in AUG and JET}
    \item Do we observe same behavior in L and H-Mode? \alert{So
      far no as shown in H-Mode AUG. We need higher detachment
      condition and we need enough fueling}
      \item What are the underlying mechanisms? 
    \end{enumerate}
  \end{frame}

\section{Topic 21 experiments }
\begin{frame}{more proposed shots than allocated}
	\begin{itemize}
		\item totla number propose shots 449
		\item ebven though combined we have to prioritize
		\item prioritize cross comparison 
		\item 
	\end{itemize}
\end{frame}

@@

>>>>

  \section{Open issues}
  \begin{frame}{Open and unresolved issues}
  \setbeamercovered{transparent}
  \begin{enumerate}[<+(1) | invisible@-+>]
    \item Does $\Lambda_{div}$ unify the picture among the devices?
      \alert{No, a dependence on neutral pressure is likely to play a role}
    \item If neutrals play a role is it at the divertor and/or at the midplane?
      \alert{Contradictory results if one include experiments with
        midplane puffing, JET and EIRENE simulations}
    \item Does L$_\parallel$ play any role? \alert{So far TCV suggests no
      dependence from f$_x$ scan but both TCV and MAST observe an
      I$_p$ dependence. MAST clearly state filament $\sigma_{\perp}$
      increases with L$_{\parallel}$ }
    \item Is cooling the divertor with fueling or with equivalent? \alert{Contradictory observations in AUG and JET}
    \item Do we observe same behavior in L and H-Mode? \alert{So
      far no as shown in H-Mode AUG. We need higher detachment
      condition and we need enough fueling}
      \item What are the underlying mechanisms? 
    \end{enumerate}
  \end{frame}

\section{Topic 21 experiments }
\begin{frame}{$n_{\text{proposed shots}} \gg n_{\text{allocated shots}}$}
	\begin{itemize}
		\item 15 proposals submitted to Topic 21
		\item Proposals include experiments on all three machines 
		\item There are overlaps between several of the proposals 
		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23
		\item However, total number of proposed shots:  \textbf{449}
		\item \underline{We must prioritize}
		\item

	\end{itemize}
\end{frame}

@@

\end{frame}

\begin{frame}{Proposed shot plan}
	piggybaggers (Mclements, relfectometry guys)

	COMPASS
\end{frame}

\begin{frame}{Discussion agenda}

\end{frame}

\begin{frame}{Future}
	meetings

	wiki
